### 2016-07-01 store-consistency.tex
edits

\paragraph{Discussion.} As evident from the example, instantiating the
proof system for a specfic combination of consistency and isolation
settings, and then deriving facts specific to that setting
characterizes our reasoning approach. While intuition suggests that
some instantiations, such as {\sc sc} with ANSI SQL isolation, are
general enough to cover many practical cases, it not the case in
reality owing to the subtle differences in the semantics of isolation
levels among databases. For instance, Postgres's \iso{Repeatable Read}
isolation is stronger than ANSI SQL's or MySQL's in non-trivial ways.
Furthermore, the need for high availability on geo-replicated stores
has led to the development of of new isolation levels which are yet to
be standardized. For example, \emph{Parallel Snapshot
Isolation}~\cite{psi} was proposed in 2011, and \emph{Non-Monotonic
Snapshot Isolation}~\cite{nmsi} in 2013, both targeted for replicated
stores. As more commercial weakly consistent stores adopt variants of
transactions (like the \emph{lightweight transactions} of Cassandra),
it is reasonable to expect novel forms of isolation to be proposed.
While it is possible to carefully engineer a reasoning framework for
each combination of consistency and isolation, it leads to multiple
proof systems with no obvious to compare proofs.  Having a
parameterized semantics and proof framework built on this semantics
allows us to support these variants as distinct, yet comparable
instantiations, thus avoiding the need for semantics re-engineering
every time an application is retargeted to a new platform

>>>>

\paragraph{Discussion.} As evident from the example, instantiating the
proof system for a specfic combination of consistency and isolation
settings, and then deriving facts specific to that setting
characterizes our reasoning approach. While intuition suggests that
some instantiations, such as {\sc sc} with ANSI SQL isolation, are
general enough to cover many practical cases, it not the case in
reality given the subtle differences in the semantics of isolation
levels among different database implementations. For instance,
Postgres' \iso{Repeatable Read} isolation is stronger than ANSI SQL's
or MySQL's in non-trivial ways.  Furthermore, the need for high
availability on geo-replicated stores has led to the development of
new isolation levels which are yet to be standardized. For example,
\emph{Parallel Snapshot Isolation}~\cite{psi} was proposed in 2011,
and \emph{Non-Monotonic Snapshot Isolation}~\cite{nmsi} in 2013, both
targeted for replicated stores. As more commercial weakly consistent
stores adopt variants of transactions, like the recently introduced
\emph{lightweight transactions} of Cassandra, it is reasonable to
expect new isolation definitions to continue to be proposed.  While it
is possible to carefully engineer a reasoning framework for each
combination of consistency and isolation, such a strategy would lead
to multiple semantic definitions and proof systems with no obvious to
compare and relate them.  Having a parameterized semantics and proof
framework built on the framework defined above allows us to support
these variants as distinct, yet comparable instantiations, thus
avoiding the need for semantics re-engineering every time an
application is retargeted to a new platform.
